Submissions and selectivity of *eLife* over time.

### 2019-02-19 figures/gatekeeper_representation/reviewing_editor_continental_composition.rmd

### Set parameters for the name and extension of the figure
```{r}
figure_name <- "fig_si6"
figure_extension <- ".png"

path_to_data <- "https://www.dropbox.com/s/5doa2khbrs7nuyx/formatted_elife.csv?dl=1"
```

@@

```{r}
continental_composition <- elife %>%
  filter(has_full_submission & full_decision_made & !is.na(bre_continent)) %>%
  group_by(MSNO) %>%
  mutate(
    num_africa = sum(na.omit(c(reviewer1_continent, reviewer2_continent, reviewer3_continent, reviewer4_continent)) == 1),
    contains_africa = ifelse(bre_is_reviewer & bre_continent == "Africa", num_africa > 1, num_africa > 0),
    num_asia = sum(na.omit(c(reviewer1_continent, reviewer2_continent, reviewer3_continent, reviewer4_continent)) == 2),
    contains_asia = ifelse(bre_is_reviewer & bre_continent == "Asia", num_asia > 1, num_asia > 0),
    num_na = sum(na.omit(c(reviewer1_continent, reviewer2_continent, reviewer3_continent, reviewer4_continent)) == 4),
    contains_na = ifelse(bre_is_reviewer & bre_continent == "North America", num_na > 1, num_na > 0),
    num_eu = sum(na.omit(c(reviewer1_continent, reviewer2_continent, reviewer3_continent, reviewer4_continent)) == 3),
    contains_eu = ifelse(bre_is_reviewer & bre_continent == "Europe", num_eu > 1, num_eu > 0),
    num_sa = sum(na.omit(c(reviewer1_continent, reviewer2_continent, reviewer3_continent, reviewer4_continent)) == 6),
    contains_sa = ifelse(bre_is_reviewer & bre_continent == "South America", num_sa > 1, num_sa > 0),
    num_oceania = sum(na.omit(c(reviewer1_continent, reviewer2_continent, reviewer3_continent, reviewer4_continent)) == 5),
    contains_oceania = ifelse(bre_is_reviewer & bre_continent == "Oceania", num_oceania > 1, num_oceania > 0)
  ) %>%
  group_by(bre_continent) %>%
  mutate(total = n()) %>%
  gather(contains_key, contains, contains_africa, contains_asia, contains_na, contains_eu, contains_sa, contains_oceania) %>%
  group_by(contains_key, contains, bre_continent) %>%
  summarize(
    prop = n() / total[1]
  ) %>%
  ungroup() %>%
  mutate(
    bre_continent = factor(bre_continent, levels = c("North America", "Europe", "Asia", "Oceania", "South America", "Africa")),
    contains_key = factor(contains_key, 
                          levels = c("contains_na", "contains_eu", "contains_asia", "contains_oceania", "contains_sa", "contains_africa"),
                          labels = c("contains_na" = "North America", "contains_eu" = "Europe", 
                                     "contains_asia" = "Asia", "contains_oceania" = "Oceania", 
                                     "contains_sa" = "South America", "contains_africa" = "Africa"))
  ) %>%
  filter(contains == T) %>%
  ggplot(aes(x = contains_key, y = prop, fill = contains_key)) +
  geom_bar(stat = "identity", color = "black", alpha = 0.8) +
  facet_wrap(~bre_continent, ncol = 6) +
  geom_text(aes(label = paste0(round(prop, 3) * 100, "%"), y = prop + 0.025), size = 2) +
  theme_dakota() +
  scale_fill_brewer(palette = "Blues", direction = -1) +
  ylim(0, 1.0) +
   guides(fill = F) +
  theme(
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)
  ) +
  labs(y = "Proportion",
       x = "Composition of invited peer reviewer teams"
       )

>>>>

### Set parameters for the name and extension of the figure
```{r}
figure_name <- "fig_si6"
figure_extension <- ".pdf"

path_to_data <- "https://www.dropbox.com/s/97im2cayb1trlax/formatted_elife.csv?dl=1"
```

@@

```{r}
continental_composition <- elife %>%
  filter(has_full_submission & full_decision_made & !is.na(bre_continent)) %>%
  group_by(MSNO) %>%
  mutate(
    num_africa = sum(na.omit(c(reviewer1_continent, reviewer2_continent, reviewer3_continent, reviewer4_continent)) == "Africa"),
    contains_africa = ifelse(bre_is_reviewer & bre_continent == "Africa", num_africa > 1, num_africa > 0),
    num_asia = sum(na.omit(c(reviewer1_continent, reviewer2_continent, reviewer3_continent, reviewer4_continent)) == "Asia"),
    contains_asia = ifelse(bre_is_reviewer & bre_continent == "Asia", num_asia > 1, num_asia > 0),
    num_na = sum(na.omit(c(reviewer1_continent, reviewer2_continent, reviewer3_continent, reviewer4_continent)) == "North America"),
    contains_na = ifelse(bre_is_reviewer & bre_continent == "North America", num_na > 1, num_na > 0),
    num_eu = sum(na.omit(c(reviewer1_continent, reviewer2_continent, reviewer3_continent, reviewer4_continent)) == "Europe"),
    contains_eu = ifelse(bre_is_reviewer & bre_continent == "Europe", num_eu > 1, num_eu > 0),
    num_sa = sum(na.omit(c(reviewer1_continent, reviewer2_continent, reviewer3_continent, reviewer4_continent)) == "South America"),
    contains_sa = ifelse(bre_is_reviewer & bre_continent == "South America", num_sa > 1, num_sa > 0),
    num_oceania = sum(na.omit(c(reviewer1_continent, reviewer2_continent, reviewer3_continent, reviewer4_continent)) == "Oceania"),
    contains_oceania = ifelse(bre_is_reviewer & bre_continent == "Oceania", num_oceania > 1, num_oceania > 0)
  ) %>%
  group_by(bre_continent) %>%
  mutate(total = n()) %>%
  gather(contains_key, contains, contains_africa, contains_asia, contains_na, contains_eu, contains_sa, contains_oceania) %>%
  group_by(contains_key, contains, bre_continent) %>%
  summarize(
    prop = n() / total[1]
  ) %>%
  ungroup() %>%
  mutate(
    bre_continent = factor(bre_continent, levels = c("North America", "Europe", "Asia", "Oceania", "South America", "Africa")),
    contains_key = factor(contains_key, 
                          levels = c("contains_na", "contains_eu", "contains_asia", "contains_oceania", "contains_sa", "contains_africa"),
                          labels = c("contains_na" = "North America", "contains_eu" = "Europe", 
                                     "contains_asia" = "Asia", "contains_oceania" = "Oceania", 
                                     "contains_sa" = "South America", "contains_africa" = "Africa"))
  ) %>%
  filter(contains == T) %>%
  ggplot(aes(x = contains_key, y = prop, fill = contains_key)) +
  geom_bar(stat = "identity", color = "black", alpha = 0.8) +
  facet_wrap(~bre_continent, ncol = 6) +
  geom_text(aes(label = paste0(round(prop, 3) * 100, "%"), y = prop + 0.025), size = 2) +
  theme_dakota() +
  scale_fill_brewer(palette = "Blues", direction = -1) +
  ylim(0, 1.0) +
   guides(fill = F) +
  theme(
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)
  ) +
  labs(y = "Proportion",
       x = "Composition of invited peer reviewer teams"
       )

### 2019-02-19 figures/regression_analysis/regression_analysis_simple.rmd

### Set parameters for the name and extension of the figure
```{r}
figure_name <- "fig_6"
figure_extension <- ".png"

@@

```{r}
initial.cov.labels = c("submission_year" = "Submission Year", 
               "submission_typeSR" = "Submission Type = SR", 
               "submission_typeTR" = "Submission Type = TR", 
               "ca_genderM" = "Corr. Author is Male",
               "ca_genderUNK" = "Corr. Author Gender UNK",
               "ca_institution_rankTop" = "Corr. Author Inst. Top 50",
               "ca_institution_rankStandard/Unranked/Unknown" = "Corr. Author Inst. Below 200",
               "ca_continentAfrica" = "Corr. author from Africa",
               "ca_continentAsia" = "Corr. author from Asia",
               "ca_continentEurope" = "Corr. author from Europe",
               "ca_continentOceania" = "Corr. author from Oceania",
               "ca_continentSouth America" = "Corr. author from South America",
               "se_genderM" = "Senior Editor is Male",
               "I(ca_se_dist/1e+06)" = "Geographic distance (1000s km)",
               "ca_se_dist_zeroTRUE" = "Geographic distance is zero",
               "ca_genderM:se_genderM" = "Corr. author male * Senior editor male",
               "ca_genderUNK:se_genderM" = "Corr. author UNK * Senior editor male"

               )

out <- capture.output(stargazer(initial_model, 
                                ci = T, 
                                align = T,
                                covariate.labels = initial.cov.labels, 
                                model.names = T,
                                style = "ajs"
                                ))

out
#cat(paste(out, collapse = "\n"), "\n", file="~/Desktop/encourage_model.txt", append=F)
```

@@

### Construct a table for the regression model for full submissions
```{r}
full.cov.labels = c("submission_year" = "Submission Year", 
               "submission_typeSR" = "Submission Type = SR", 
               "submission_typeTR" = "Submission Type = TR", 
               "fa_genderM" = "First Author is Male",
               "fa_genderUNK" = "First Author is Unknown Gender",
               "la_genderM" = "Last Author is Male",
               "la_institution_rankTop" = "Last Author Inst. Top 50",
               "la_continentAfrica" = "Last author from Africa",
               "la_continentAsia" = "Last author from Asia",
               "la_continentEurope" = "Last author from Europe",
               "la_continentOceania" = "Last author from Oceania",
               "la_continentSouth America" = "Last author from South America"
               )

out <- capture.output(stargazer(full_model, 
                                ci = T, 
                                align = T, 
                                covariate.labels = full.cov.labels, 
                                model.names = T,
                                style = "ajs",
                                font.size = "scriptsize"
                                ))

out
#cat(paste(out, collapse = "\n"), "\n", file="~/Desktop/accept_model.txt", append=TRUE)
```

@@

### Arrange graphs
```{r}
regressions_simple <- grid.arrange(initial_reg_plot, full_reg_plot, ncol = 2)
plot(regressions_simple)
```

### Save the output
```{r}
name <- paste0("~/Dropbox/eLife/elife-analysis/figures/main/", figure_name, figure_extension)
ggsave(name, plot = regressions_simple, height = 5, width = 10)
```

>>>>

### Set parameters for the name and extension of the figure
```{r}
figure_name <- "fig_6"
figure_extension <- ".pdf"

@@

```{r}
initial.cov.labels = c(
               "submission_year" = "Submission Year", 
               "submission_typeSR" = "Submission Type = SR", 
               "submission_typeTR" = "Submission Type = TR", 
               "ca_genderM" = "Corr. Author is Male",
               "ca_genderUNK" = "Corr. Author Gender UNK",
               "ca_institution_rankTop" = "Corr. Author Inst. Top",
               "ca_continentAfrica" = "Corr. author from Africa",
               "ca_continentAsia" = "Corr. author from Asia",
               "ca_continentEurope" = "Corr. author from Europe",
               "ca_continentOceania" = "Corr. author from Oceania",
               "ca_continentSouth America" = "Corr. author from South America"
               )

stargazer(initial_model, 
          ci = T, 
          align = T,
          t.auto = F,
          p.auto = F,
          apply.coef = exp,
          covariate.labels = initial.cov.labels, 
          model.names = T,
          style = "ajs",
          type = "latex"
          )

#cat(paste(out, collapse = "\n"), "\n", file="~/Desktop/encourage_model.txt", append=F)
```

@@

### Construct a table for the regression model for full submissions
```{r}
full.cov.labels = c("submission_year" = "Submission Year", 
               "submission_typeSR" = "Submission Type = SR", 
               "submission_typeTR" = "Submission Type = TR", 
               "fa_genderM" = "First Author is Male",
               "fa_genderUNK" = "First Author is Unknown Gender",
               "la_genderM" = "Last Author is Male",
               "la_institution_rankTop" = "Last Author Inst. Top",
               "la_continentAfrica" = "Last author from Africa",
               "la_continentAsia" = "Last author from Asia",
               "la_continentEurope" = "Last author from Europe",
               "la_continentOceania" = "Last author from Oceania",
               "la_continentSouth America" = "Last author from South America"
               )

stargazer(full_model, 
          ci = T, 
          align = T, 
          t.auto = F,
          p.auto = F,
          apply.coef = exp,
          covariate.labels = full.cov.labels, 
          model.names = T,
          style = "ajs",
          font.size = "scriptsize",
          type = "latex"
          )

#out
#cat(paste(out, collapse = "\n"), "\n", file="~/Desktop/accept_model.txt", append=TRUE)
```

@@

### Arrange graphs
```{r}
regressions_simple <- grid.arrange(initial_reg_plot, full_reg_plot, ncol = 2)
```

### Save the output
```{r}
name <- paste0("~/Dropbox/eLife/elife-analysis/figures/main/", figure_name, figure_extension)
ggsave(name, plot = regressions_simple, height = 6, width = 10)
```

### 2019-02-19 figures/regression_analysis/regression_bre_only_analysis.rmd

---
title: "Regression Analysis—Interactions"
author: "Dakota Murray"
output: html_notebook
---

### Set parameters for the name and extension of the figure
```{r}
figure_name <- "fig_7"
figure_extension <- ".pdf"

@@

### Construct a regression table for the 
```{r}
initial.cov.labels = c("submission_year" = "Submission Year", 
               "submission_typeSR" = "Submission Type = SR", 
               "submission_typeTR" = "Submission Type = TR", 
               "ca_genderM" = "Corr. Author is Male",
               "ca_genderUNK" = "Corr. Author Gender UNK",
               "ca_institution_rankTop" = "Corr. Author Inst. Top",
               "ca_continentAfrica" = "Corr. author from Africa",
               "ca_continentAsia" = "Corr. author from Asia",
               "ca_continentEurope" = "Corr. author from Europe",
               "ca_continentOceania" = "Corr. author from Oceania",
               "ca_continentSouth America" = "Corr. author from South America",
               "I(ca_se_dist/1e+06)" = "Geographic distance (1000s km)",
               "ca_se_dist_zeroTRUE" = "Geographic distance is zero"
               )

stargazer(initial_model, 
            ci = T, 
            t.auto = F,
            p.auto = F,
            align = T, 
            apply.coef = exp,
            covariate.labels = initial.cov.labels, 
            model.names = T,
            style = "ajs"
            )

#cat(paste(out, collapse = "\n"), "\n", file="~/Desktop/encourage_model.txt", append=F)
#out
```

@@

### Construct the interaction variable
```{r}
assign_interaction_term = function(la_gender, composition) {
  if (la_gender == "M") {
    if (composition == "All Men") {
      return("Male Author, All Men")
    } else if (composition == "All Women") {
      return("Male Author, All Women")
    } else if (composition == "Mixed") {
      return("Male Author, Mixed")
    } else {
      return(NA)
    }
  } else if (la_gender == "F") {
    if (composition == "All Men") {
      return("Female Author, All Men")
    } else if (composition == "All Women") {
      return("Female Author, All Women")
    } else if (composition == "Mixed") {
      return("Female Author, Mixed")
    } else {
      return(NA)
    }
  } else {
    return(NA)
  }
}

full_with_inter <- full_submissions %>%
  filter(composition != "Uncertain") %>%
  rowwise() %>%
  mutate(
    author_reviewer_interaction = assign_interaction_term(la_gender, composition)
  ) %>%
  ungroup() %>%
  mutate(author_reviewer_interaction = as.factor(author_reviewer_interaction))

table(full_with_inter$author_reviewer_interaction)
```

### Construct the model for full submissions with interactions
```{r}
full_model <- glm(accepted ~ submission_year + submission_type + fa_gender + la_institution_rank + la_continent + I(la_reviewer_dist/ 1000000) + la_reviewer_dist_zero + author_reviewer_interaction, data = subset(full_with_inter, included), family = "binomial")
summary(full_model)
```

@@

### Construct the plot for full submissions
```{r}
full.cov.labels = c("submission_year" = "Submission Year", 
               "submission_typeSR" = "Submission Type = SR", 
               "submission_typeTR" = "Submission Type = TR", 
               "fa_genderM" = "First Author is Male",
               "fa_genderUNK" = "First Author is Unknown Gender",
               "la_institution_rankTop" = "Last Author Inst. Top",
               "la_continentAfrica" = "Last author from Africa",
               "la_continentAsia" = "Last author from Asia",
               "la_continentEurope" = "Last author from Europe",
               "la_continentOceania" = "Last author from Oceania",
               "la_continentSouth America" = "Last author from South America",
               "I(la_reviewer_dist/1e+06)" = "Sum of geographic distance (1000s km)",
               "la_reviewer_dist_zeroTRUE" = "Sum of geographic distance is zero",
               "author_reviewer_interactionFemale Author, All Women" = "Last author female - all reviewers female",
               "author_reviewer_interactionFemale Author, Mixed" = "Last author female - mixed reviewers",
               "author_reviewer_interactionMale Author, All Men" = "Last author male - all reviewers male",
               "author_reviewer_interactionMale Author, All Women" = "Last author male - all reviewers female",
               "author_reviewer_interactionMale Author, Mixed" = "Last author male - mixed reviewers"
               )

stargazer(full_model, 
          ci = T, 
          align = T, 
          apply.coef = exp,
          t.auto = F,
          p.auto = F,
          covariate.labels = full.cov.labels, 
          model.names = T,
          style = "ajs",
          font.size = "scriptsize"
          )

#cat(paste(out, collapse = "\n"), "\n", file="~/Desktop/full_model.txt", append=F)
#out

```

```{r}
full_reg_plot <- plot_model(full_model, 
           vline.color = "black", 
           rm.terms = c("fa_genderUNK"),
           sort.est = TRUE, 
           show.values = TRUE, 
           value.offset = .4, 
           axis.labels = full.cov.labels,
           wrap.labels = 100, # basically, don't wrap the labels, squeeze them all in
           title = "Acceptance of full submissions",
           axis.lim = c(0.1, 10)) +
  theme_bw()

@@

@@

### Save the plot
```{r}
name <- paste0("~/Dropbox/eLife/elife-analysis/figures/main/", figure_name, figure_extension)
ggsave(name, plot = regressions_interactions, height = 8, width = 10)
```

>>>>

---
title: "Regression Analysis—Interactions—Reviewing Editor"
author: "Dakota Murray"
output: html_notebook
---

### Set parameters for the name and extension of the figure
```{r}
figure_name <- "fig_si.X"
figure_extension <- ".png"

@@

### Construct a regression table for the 
```{r}
initial.cov.labels = c("submission_year" = "Submission Year", 
               "submission_typeSR" = "Submission Type = SR", 
               "submission_typeTR" = "Submission Type = TR", 
               "ca_genderM" = "Corr. Author is Male",
               "ca_genderUNK" = "Corr. Author Gender UNK",
               "ca_institution_rankTop" = "Corr. Author Inst. Top 50",
               "ca_institution_rankStandard/Unranked/Unknown" = "Corr. Author Inst. Below 200",
               "ca_continentAfrica" = "Corr. author from Africa",
               "ca_continentAsia" = "Corr. author from Asia",
               "ca_continentEurope" = "Corr. author from Europe",
               "ca_continentOceania" = "Corr. author from Oceania",
               "ca_continentSouth America" = "Corr. author from South America",
               "se_genderM" = "Senior Editor is Male",
               "I(ca_se_dist/1e+06)" = "Geographic distance (1000s km)",
               "ca_se_dist_zeroTRUE" = "Geographic distance is zero",
               "ca_genderM:se_genderM" = "Corr. author male * Senior editor male",
               "ca_genderUNK:se_genderM" = "Corr. author UNK * Senior editor male"

               )

out <- capture.output(stargazer(initial_model, 
                                ci = T, 
                                align = T, 
                                covariate.labels = initial.cov.labels, 
                                model.names = T,
                                style = "ajs"
                                ))

#cat(paste(out, collapse = "\n"), "\n", file="~/Desktop/encourage_model.txt", append=F)
out
```

@@

### Construct the interaction variable
```{r}
assign_interaction_term = function(la_gender, bre_gender) {
  if (la_gender == "M") {
    if (bre_gender == "M") {
      return("Male Author, Male Rev. Editor")
    } else if (bre_gender == "F") {
      return("Male Author, Female Rev. Editor")
    } else {
      return(NA)
    }
  } else if (la_gender == "F") {
    if (bre_gender == "M") {
      return("Female Author, Male Rev. Editor")
    } else if (bre_gender == "F") {
      return("Female Author, Female Rev. Editor")
    } else {
      return(NA)
    }
  } else {
    return(NA)
  }
}

full_with_inter <- full_submissions %>%
  filter(!is.na(bre_gender) & composition_adj != "Uncertain") %>%
  rowwise() %>%
  mutate(
    author_bre_interaction = assign_interaction_term(la_gender, bre_gender)
  ) %>%
  ungroup() %>%
  mutate(author_bre_interaction = as.factor(author_bre_interaction)) %>%
  mutate(la_bre_dist_zero = la_bre_dist == 0)

table(full_with_inter$author_bre_interaction)
```

### Construct the model for full submissions with interactions
```{r}
full_model <- glm(accepted ~ submission_year + submission_type + fa_gender + la_institution_rank + la_continent + I(la_bre_dist/ 1000000) + I(la_reviewer_dist / 1000000) + la_reviewer_dist_zero + la_bre_dist_zero + author_bre_interaction + composition_adj, data = subset(full_with_inter, included), family = "binomial")
summary(full_model)
```

@@

### Construct the plot for full submissions
```{r}
full.cov.labels = c("submission_year" = "Submission Year", 
               "submission_typeSR" = "Submission Type = SR", 
               "submission_typeTR" = "Submission Type = TR", 
               "fa_genderM" = "First Author is Male",
               "fa_genderUNK" = "First Author is Unknown Gender",
               "la_institution_rankStandard/Unranked/Unknown" = "Last Author Inst. Below 200",
               "la_institution_rankTop" = "Last Author Inst. Top 50",
               "la_continentAfrica" = "Last author from Africa",
               "la_continentAsia" = "Last author from Asia",
               "la_continentEurope" = "Last author from Europe",
               "la_continentOceania" = "Last author from Oceania",
               "la_continentSouth America" = "Last author from South America",
               "I(la_bre_dist/1e+06)" = "Dist. between author and rev. editor (1000km)",
               "I(la_reviewer_dist/1e+06)" = "Sum of author-reviewer distance (1000km)",
               "la_reviewer_dist_zeroTRUE" = "Total dist. between author and reviewers is zero",
               "la_bre_dist_zeroTRUE" = "Dist. between author and rev. editor is zero",
               "author_bre_interactionFemale Author, Male Rev. Editor" = "Last author female - male rev. editor",
               "author_bre_interactionFemale Author, Female Rev. Editor" = "Last author female - female rev. editor",
               "author_bre_interactionMale Author, Female Rev. Editor" = "Last author male - female rev. editor",
               "author_bre_interactionMale Author, Male Rev. Editor" = "Last author male - male rev. editor",
               "composition_adjAll Women" = "All Female Reviewers",
               "composition_adjMixed" = "Mixed Reviewers"
               )

full_reg_plot <- plot_model(full_model, 
           vline.color = "black", 
           rm.terms = c("fa_genderUNK"),
           sort.est = TRUE, 
           show.values = TRUE, 
           value.offset = .3, 
           axis.labels = full.cov.labels,
           wrap.labels = 100, # basically, don't wrap the labels, squeeze them all in
           title = "Acceptance of full submissions",
           axis.lim = c(0.1, 10)) +
  theme_bw()

@@

```{r}
library(stargazer)
stargazer(full_model,
          covariate.labels = full.cov.labels,
          t.auto = F,
          p.auto = F,
          type = "latex",
          font.size = "small",
          style = "ajs")
```

@@

### Save the plot
```{r}
name <- paste0("~/Dropbox/eLife/elife-analysis/figures/main/", figure_name, figure_extension)
ggsave(name, plot = regressions_interactions, height = 5, width = 10)
```

### 2019-02-19 figures/selectivity_over_time/country_composition_shift.rmd

---
title: "Submissions and outcomes—16 countries"
author: "Dakota Murray"
output: html_notebook
---

### Set parameters for the name and extension of the figure
```{r}
figure_name <- "fig_si4"
figure_extension <- ".pdf"

@@

## Figure SI.4

>Figure SI.4 Top: proportion of all initial submissions, encouraged initial submissions, and accepted full submissions comprised by the national affiliation of the corresponding author for the top sixteen most prolific countries in terms of initial submissions. Bottom: acceptance rate of full submissions, encourage rate of full submissions, and overall accept rate of full submissions by national affiliation of the corresponding author for the top eight more prolific countries in terms of initial submissions. Error bars on bottom panel indicate standard error of proportion of encouraged initial submissions and accepted initial and full submissions for each country.

```{r message=FALSE, warning=FALSE}
# Its easiest and most efficient to calculate these total values outside of the dplyr chain below
total_submissions <- length(unique(elife$MSNO))
total_full_submissions <- sum(!elife$full_decision_date_isNA, na.rm = T)
total_encouraged <- with(elife, sum(initial_decision_made & encouraged, na.rm = T))
total_accepted <- with(elife, sum(full_decision_made & accepted == T, na.rm = T))

# Firs the first plot, this one will show the proportion that each countrie constitutes the total number of submitted, encouraged, and accepted manuscripts
p1 <- elife %>%
  filter(initial_decision_made & (full_decision_made | full_decision_date_isNA) & !is.na(ca_country)) %>%
  mutate(ca_country = factor(sapply(as.character(ca_country), simpleCap))) %>% # capitalize first letter of country stirngs
  group_by(ca_country) %>%
  summarize(
    paper_count = n(),
    accept_count = sum(accepted == TRUE, na.rm = T),
    encourage_count = sum(encouraged == TRUE, na.rm = T),
    full_submissions = sum(has_full_submission),
    prop_of_full =  full_submissions / total_full_submissions,
    prop_of_initial = paper_count / total_submissions,
    prop_of_encouraged = encourage_count / total_encouraged,
    prop_of_accepted = accept_count / total_accepted
  ) %>%
  group_by(ca_country) %>%
  mutate(totals = sum(paper_count)) %>%
  ungroup() %>%
  top_n(16, totals) %>%
  gather(prop_key, value = prop, prop_of_initial, prop_of_full, prop_of_accepted) %>%
  mutate(prop_key = factor(prop_key, 
                           levels = c("prop_of_initial", "prop_of_full", "prop_of_accepted"),
                           labels = c("prop_of_initial" = "Prop. of initial submissions", 
                                      "prop_of_full" = "Prop. of full submissions", 
                                      "prop_of_accepted" = "Prop. of accepted submissions")),
         ca_country = reorder(ca_country, paper_count)
  ) %>%
  # Start ggplot
  ggplot(aes(x = ca_country, y = prop)) +
  geom_bar(stat = "identity", color = "black", alpha = 0.8, fill = "dodgerblue4", position = position_dodge(1)) +
  geom_text(aes(y = prop, label = paste0(round(prop, 3) * 100, "%")), size = 2.5, hjust = -0.2, family = "Times", position = position_dodge(1)) +
  scale_y_continuous(limits = c(0, 1)) +
  facet_wrap(~prop_key, labeller = labeller(key = labels)) +
  theme_dakota() +
  coord_flip() +
  ylim(0, 0.7) +
  labs(y = "") +
  theme(
    strip.background = element_blank(),
    text = element_text(size = 10, family = "Times"),
    plot.title = element_text(size = 12),
    strip.text = element_text(face = "bold"),
    axis.title.y = element_blank()
  )

p2 <- elife %>%
  filter(initial_decision_made & (full_decision_made | full_decision_date_isNA) & !is.na(ca_country)) %>%
  mutate(ca_country = factor(sapply(as.character(ca_country), simpleCap))) %>% # capitalize first letter of country stirngs
  group_by(ca_country) %>%
  summarize(
    paper_count = n(),
    accept_count = sum(accepted == TRUE, na.rm = T),
    encourage_count = sum(encouraged == TRUE, na.rm = T),
    encourage_rate = encourage_count / paper_count,
    accept_rate = accept_count / sum(!has_full_submission | full_decision_made, na.rm = T),
    encourage_accept_rate = accept_count / sum(has_full_submission & full_decision_made, na.rm = T)
  ) %>%
  group_by(ca_country) %>%
  mutate(totals = sum(paper_count)) %>%
  ungroup() %>%
  top_n(16, totals) %>%
  mutate(
    ca_country = reorder(ca_country, encourage_rate)
  ) %>%
  gather(measure_key, value = measurement, encourage_rate, accept_rate, encourage_accept_rate) %>%
  mutate(measure_key = factor(measure_key, 
                           levels = c("encourage_rate", "encourage_accept_rate", "accept_rate"),
                           labels = c("encourage_rate" = "% of initial submissions encouraged", 
                                      "encourage_accept_rate" = "% of full submissions accepted",
                                      "accept_rate" = "% of initial submissions accepted"
                                      )
                           ) # end factor
  ) %>%
  group_by(measure_key) %>%
  mutate(
    se = 1.96 * sqrt(measurement * (1 - measurement) / paper_count),
    lower = measurement - se,
    upper = measurement + se
  ) %>%
  ggplot(aes(x = ca_country, y = measurement)) +
  geom_bar(stat = "identity", color = "black", fill = "dodgerblue4", alpha = 0.8) +
  geom_text(aes(y = upper, label = paste0(round(measurement, 3) * 100, "%")), size = 2.5, hjust = -0.4, family = "Times") +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2) +
  facet_wrap(~measure_key, labeller = labeller(key = labels)) +
  theme_dakota() +
  labs(y = "%") +
  coord_flip() +
  ylim(0, 0.75) +
  theme(
    axis.title.y = element_blank()
  )

countries_16 <- grid.arrange(p1, p2)
plot(countries_16)
```

### Save the file
```{r}
## Save the file
name <- paste0("~/Dropbox/eLife/elife-analysis/figures/supp/", figure_name, figure_extension)
ggsave(name, plot = countries_16, height = 6, width = 10)
```

>>>>

---
title: "Country Submissions Over Time"
author: "Dakota Murray"
output: html_notebook
---

### Set parameters for the name and extension of the figure
```{r}
figure_name <- "fig_si9"
figure_extension <- ".pdf"

@@

```{r}
country_over_time <- elife %>%
  #mutate(submission_year = submission_year + 2012) %>%
  filter(submission_year <= 2016 & !is.na(ca_continent)) %>%
  group_by(submission_year, ca_continent) %>%
  summarize(
    count = n()
  ) %>%
  ggplot(aes(x = submission_year, y = count, color = ca_continent, shape = ca_continent)) +
  geom_line() +
  geom_point() +
  theme_dakota() +
  labs(x = "Year",
       y = "# Submissions")

country_over_time
```

```{r}
country_over_time <- elife %>%
  filter(has_full_submission) %>%
  #mutate(submission_year = submission_year + 2012) %>%
  filter(submission_year <= 2016 & !is.na(ca_continent)) %>%
  group_by(submission_year, ca_continent) %>%
  summarize(
    count = n()
  ) %>%
  ggplot(aes(x = submission_year, y = count, color = ca_continent, shape = ca_continent)) +
  geom_line() +
  geom_point() +
  theme_dakota() +
  labs(x = "Year",
       y = "# Submissions")

country_over_time
```

### Save the file
```{r}
## Save the file
name <- paste0("~/Dropbox/eLife/elife-analysis/figures/supp/", figure_name, figure_extension)
ggsave(name, plot = country_over_time, height = 6, width = 10)
```

### 2019-02-19 figures/selectivity_over_time/selectivity_over_time.rmd

### Set parameters for the name and extension of the figure
```{r}
figure_name <- "fig_2"
figure_extension <- ".png"

path_to_data <- "https://www.dropbox.com/s/5doa2khbrs7nuyx/formatted_elife.csv?dl=1"
```

>>>>

### Set parameters for the name and extension of the figure
```{r}
figure_name <- "fig_2"
figure_extension <- ".pdf"

path_to_data <- "https://www.dropbox.com/s/u5lmsyri359mvr9/formatted_elife.csv?dl=1"
```
